analisis-preliminar

### 2021-04-14 production/analisis-preliminar.Rmd
Se agrega información de las versiones de los paquetes

```{r}
pacman::p_load(stargazer, ggplot2, sjmisc, car, sjlabelled, haven, cowplot,
               sjPlot, summarytools, kableExtra, corrplot, coefplot, ltm, polycor,
               psych, lme4, ppcor, texreg, skimr, dplyr)
```

>>>>

```{r}
pacman::p_load(stargazer, ggplot2, sjmisc, car, sjlabelled, haven, cowplot,
               sjPlot, summarytools, kableExtra, corrplot, coefplot, ltm, polycor,
               psych, lme4, ppcor, texreg, skimr, sessioninfo, dplyr)

##sessionInfo()
#R version 4.0.2 (2020-06-22)
#Platform: x86_64-w64-mingw32/x64 (64-bit)
#Running under: Windows 10 x64 (build 19042)

#Matrix products: default

#locale:
#[1] LC_COLLATE=Spanish_Chile.1252  LC_CTYPE=Spanish_Chile.1252    LC_MONETARY=Spanish_Chile.1252 LC_NUMERIC=C                   LC_TIME=Spanish_Chile.1252

#attached base packages:
#[1] stats     graphics  grDevices utils     datasets  methods   base

#other attached packages:
#[1] sessioninfo_1.1.1  dplyr_1.0.2        skimr_2.1.2        texreg_1.37.5      ppcor_1.1          lme4_1.1-26        Matrix_1.3-2       psych_2.0.12      
#[9] ltm_1.1-1          polycor_0.7-10     msm_1.6.8          MASS_7.3-53        coefplot_1.2.7     corrplot_0.84      kableExtra_1.3.1   summarytools_0.9.8
#[17] sjPlot_2.8.7       cowplot_1.1.1      haven_2.3.1        sjlabelled_1.1.7   car_3.0-10         carData_3.0-4      sjmisc_2.8.6       ggplot2_3.3.3     
#[25] stargazer_5.2.2 
```
